---
title: "Qno_7"
author: "Arpan Sapkota"
date: "2023-07-02"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## a
```{r, warning=FALSE}

library(car)
data("Bfox")

set.seed(07)

train_indices <- sample(1:nrow(Bfox), 0.7 * nrow(Bfox))
train_data <- Bfox[train_indices, ]
test_data <- Bfox[-train_indices, ]
```

## b
```{r, warning=FALSE}
library(caret)

linear_model <- train(debt ~ ., data = train_data, method = "lm")
knn_model <- train(debt ~ ., data = train_data, method = "knn")
```

## c
```{r, warning=FALSE}
summary(linear_model)
linear_model$results
```

These indices provide information about the model's performance, such as the average difference between predicted and actual values (RMSE), the proportion of variance explained (R-squared), and the variability of these indices across different iterations or cross-validation folds.


## d
```{r, warning=FALSE}
linear_pred <- predict(linear_model, newdata = test_data)
knn_pred <- predict(knn_model, newdata = test_data)
```

## e
```{r, warning=FALSE}
library(MLmetrics)

linear_r2 <- R2_Score(test_data$debt, linear_pred)
linear_mse <- MSE(test_data$debt, linear_pred)
linear_rmse <- RMSE(test_data$debt, linear_pred)

knn_r2 <- R2_Score(test_data$debt, knn_pred)
knn_mse <- MSE(test_data$debt, knn_pred)
knn_rmse <- RMSE(test_data$debt, knn_pred)

# Printing the fit indices
cat("Linear Regression Model:\n")
cat("R-square: ", linear_r2, "\n")
cat("Mean Squared Error (MSE): ", linear_mse, "\n")
cat("Root Mean Squared Error (RMSE): ", linear_rmse, "\n\n")

cat("KNN Regression Model:\n")
cat("R-square: ", knn_r2, "\n")
cat("Mean Squared Error (MSE): ", knn_mse, "\n")
cat("Root Mean Squared Error (RMSE): ", knn_rmse, "\n")

```
The linear regression model outperforms the KNN regression model based on these fit indices. It has a higher R-squared value and lower MSE and RMSE, indicating a better fit and more accurate predictions compared to the KNN model.